Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-05 workflow/workflow.Rmd
updated color vector in slingshot pairs plots.

```{r tree, fig.cap="Cells color-coded by cluster in a 4-dimensional MDS space with connecting lines between cluster centers representing the inferred structure."}
pairs(lineages, type="lineages", col = pal[primaryClusterNamed(ceObj)])
```

@@

pairs(lineages, type="curves", col = pal[primaryClusterNamed(ceObj)])
```

>>>>

```{r tree, fig.cap="Cells color-coded by cluster in a 4-dimensional MDS space with connecting lines between cluster centers representing the inferred structure."}
pairs(lineages, type="lineages", col = pal[cl])
```

@@

pairs(lineages, type="curves", col = pal[cl])
```
